An Open Repository of Real-Time COVID-19 Indicators

### 2021-07-12 indicators/paper/paper-medrxiv.tex
Add medRxiv version+supplement, remove Google authors temporarily

\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnasresearcharticle} % Choose template
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

@@

% Middle authors
\author[d]{Sumit Agrawal}
\author[e]{Wael Al Saeed}
\author[f]{Taylor Arnold}
\author[g]{Amartya Basu}
\author[h]{Jacob Bien}
\author[i]{{\'A}ngel A. Cabrera}
\author[b]{Andrew Chin}
\author[b]{Eu Jing Chua}
\author[b]{Brian Clark}
\author[d]{Sarah Colquhoun}
\author[b]{Nat DeFries}
\author[d]{David C. Farrow}
\author[i]{Jodi Forlizzi}
\author[d]{Jed Grabman}
\author[b]{Samuel Gratzl}
\author[a]{Alden Green}
\author[b]{George Haff}
\author[i]{Robin Han}
\author[d]{Kate Harwood}
\author[a,b]{Addison J. Hu}
\author[d]{Raphael Hyde}
\author[h]{Sangwon Hyun}
\author[e]{Ananya Joshi}
\author[j]{Jimi Kim}
\author[i]{Andrew Kuznetsov}
\author[b]{Wichada La Motte-Kerr}
\author[k]{Yeon Jin Lee}
\author[l]{Kenneth Lee}
\author[b]{Zachary C. Lipton}
\author[i]{Michael X. Liu}
\author[m]{Lester Mackey}
\author[b]{Kathryn Mazaitis}
\author[n]{Daniel J. McDonald}
\author[d]{Phillip McGuinness}
\author[o,p]{Balasubramanian Narasimhan}
\author[d]{Michael P. O'Brien}
\author[a,b]{Natalia L. Oliveira}
\author[a,b]{Pratik Patil}
\author[i]{Adam Perer}
\author[b]{Collin A. Politsch}
\author[o]{Samyak Rajanala}
\author[e]{Dawn Rucker}
\author[d]{Chris Scott}
\author[q]{Nigam H. Shah}
\author[r]{Vishnu Shankar}
\author[l]{James Sharpnack}
\author[b]{Dmitry Shemetov}
\author[s]{Noah Simon}
\author[d]{Benjamin Y. Smith}
\author[b]{Vishakha Srivastava}
\author[n]{Shuyi Tan}
\author[o,p]{Robert Tibshirani}
\author[o]{Elena Tuzhilina}
\author[b]{Ana Karina Van Nortwick}
\author[a]{Val{\'e}rie Ventura}
\author[a,b]{Larry Wasserman}
\author[d]{Benjamin Weaver}
\author[t]{Jeremy C. Weiss}
\author[d]{Spencer Whitman}
\author[i]{Kristin Williams}

@@

\affil[a]{Department of Statistics \& Data Science, Carnegie Mellon University}
\affil[b]{Machine Learning Department, Carnegie Mellon University}
\affil[c]{Computational Biology Department, Carnegie Mellon University}
\affil[d]{Google.org}
\affil[e]{Computer Science Department, Carnegie Mellon University}
\affil[f]{Linguistics Program, University of Richmond}
\affil[g]{Information Networking Institute, Carnegie Mellon University}
\affil[h]{Department of Data Sciences and Operations, University of Southern California}
\affil[i]{Human-Computer Interaction Institute, Carnegie Mellon University}
\affil[j]{School of Natural Sciences and Mathematics, University of Texas at Dallas}
\affil[k]{College of Fine Arts and Department of Psychology, Carnegie Mellon University}

@@

% Please give the surname of the lead author for the running footer
\leadauthor{Reinhart}

% Please add a significance statement to explain the relevance of your work
\significancestatement{To study the COVID-19 pandemic, its effects on society,
  and measures for reducing its spread, researchers need detailed data on the
  course of the pandemic. Standard public health data streams suffer
  inconsistent reporting and frequent, unexpected revisions. They also miss
  other aspects of a population's behavior that are worthy of consideration. We
  present an open database of COVID signals in the United States, measured at
  the county level and updated daily. This includes traditionally reported COVID
  cases and deaths, and many others: measures of mobility, social distancing,
  internet search trends, self-reported symptoms, and patterns of COVID-related
  activity in de-identified medical insurance claims. The database provides all
  signals in a common, easy-to-use format, empowering both public health
  research and operational decision-making.
}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Author contributions: A.R., L.B., M.J., A.R., J.T., A.C,
  E.J.C., N.D., D.C.F, A.J.H., S.H., M.J., J.K., W.L.M.K, Z.C.L., L.M., N.L.O.,
  J.C.W, R.R., and R.J.T. obtained and managed data;
  A.R., J.B., J.F., Z.C.L., L.M., D.J.M., A.P., S.R., D.R., C.S. N.S., R.T.,
  V.V., L.W., B.W., J.C.W, S.W., R.R., and R.J.T. designed software and
  research;
  A.R., L.B., M.J., A.R., J.T., W.A.S., T.A., A.B., J.B., L.B., A.A.C., A.C.,
  E.J.C., B.C., S.C., N.D., D.C.F., J.G., S.G., A.G., G.H., R.H., K.H., A.J.H.,
  S.H., M.J., A.J., J.K., A.K., M.X.L., L.M., K.M., D.J.M., B.N., M.P.O.,
  N.L.O., P.P., C.A.P., S.R., C.S., V.S, J.S, D.S., N.S., B.Y.S., V.S., S.T.,
  J.T., R.T., J.C.W, and R.J.T. developed software;
  S.A., W.A.S., A.C., B.C., D.C.F., S.G., G.H., K.M., D.J.M., B.N., C.S., J.S.,
  D.S., B.Y.S., and A.K.V.N. managed technical infrastructure and systems;
  A.R., L.B., M.J., A.R., J.T, J.B., A.C., E.J.C., N.D., D.C.F., A.G., K.H.,
  A.J.H., R.H., S.H., A.J., J.K., K.L., Y.J.L, Z.C.L., L.M., D.J.M., P.M., B.N.,
  N.L.O., P.P., C.A.P., S.R., N.S., V.S., J.S., D.S., N.S., S.T., J.T., R.T.,
  V.V., L.W., J.C.W., R.R., and R.J.T. performed research;
  R.R. and R.J.T. acquired funding;
  and A.R., L.B., M.J., A.R., J.T., and R.J.T. wrote the paper.
}
\authordeclaration{No competing interests to declare.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be
  addressed. E-mail: areinhar@stat.cmu.edu}
\equalauthors{\textsuperscript{2}L.B., M.J., A.R., and J.T. contributed equally
  to this work.}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{COVID-19 $|$ open data $|$ digital surveillance $|$ medical insurance
  claims $|$ internet surveys}

@@

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

\dropcap{P}ublic health decision makers, healthcare providers, epidemiological
researchers, employers, institutions, and the general public benefit from
promptly and readily accessible data regarding COVID-19 activity levels,
countermeasures, and pandemic impact.  Real-time indicators of COVID-19
activity levels, such as statistics on cases, deaths, test positivity, and
hospitalizations, enable reports and interactive dashboard applications for
situational awareness \cite{Dong:2020, NYTimes, USAFacts}, and are essential for
most analyses of the pandemic.  These data are available for locations across
the United States from a number of official sources and independent aggregators
in varied and inconsistent formats.  Different data types and sources vary in
timeliness, based on when measured events occur in the progression of the
disease, testing capabilities, the reporting pipeline, and their publication
schedules.

@@

\begin{table*}[t]
\centering
\caption{Data sources available in Delphi's COVIDcast API \cite{CovidcastAPI},
  as of date of publication. The first group of data sources are produced by
  Delphi from data not otherwise available publicly (or only available in
  limited form); the second group is mirrored from public sources.}
\begin{tabular}{>{\raggedright}p{1.2in} p{4.0in} l >{\raggedright\arraybackslash}p{0.5in}}
  \toprule
  \textbf{Data source} & \textbf{Signals available} & \textbf{First date} &
\textbf{Resolution} \\\midrule
  % Exclusive data
  Change Healthcare & Percentage of outpatient visits with COVID diagnostic
codes or codes indicating COVID-like symptoms. Based on de-identified claims
data processed by Change Healthcare. & 2020-02-01 & County$^*$ \\
  Doctor Visits & Percentage of outpatient visits primarily about COVID-like
symptoms, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^*$ \\
  Hospital Admissions & Percentage of new hospital admissions with COVID
diagnostic codes, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^{**}$\\
  Quidel & Test positivity rates for COVID-19 antigen tests produced by
Quidel. & 2020-05-26 & County$^{**}$ \\
  SafeGraph & Mobility metrics, such as time away from home or visits to bars
and restaurants, based on cell phone mobility data collected by SafeGraph
\cite{SafeGraphSocial, SafeGraphPatterns}. & 2019-01-01 & County \\
  COVID-19 Trends and Impact Survey & COVID symptoms, social distancing
behaviors, mental health, economic impact, behavior (e.g., mask-wearing,
vaccination attitudes), and COVID testing signals based on daily surveys
conducted nationally by Delphi through Facebook \cite{DelphiSurvey,
Kreuter:2020}. & 2020-04-06 & County$^{**}$ \\
  \midrule
  % Mirrored data from other sources
  Health \& Human Services & Counts of hospital admissions due to confirmed or
suspected COVID-19, as reported by the Department of Health \& Human Services. &
2019-12-31 & State \\
  COVID Act Now & COVID-19 testing results, such as positivity rate and number
of tests, compiled by COVID Act Now from CDC reporting. & 2020-03-02 &
County$^*$ \\
  Google Symptoms & Trends in Google search volume for terms related to
anosmia and ageusia (loss of smell or taste), which correlate with COVID
activity, based on data shared by Google \cite{GoogleSymptoms}. & 2020-02-13 &
County$^{***}$ \\
  Cases and Deaths & Confirmed COVID-19 cases and deaths, compiled by JHU CSSE
\cite{Dong:2020} and by USAFacts \cite{USAFacts}. & 2020-01-22 & County \\
    NCHS Mortality & Weekly totals of deaths broken down by cause, such as
COVID, flu, or pneumonia, compiled by the National Center for Health Statistics
\cite{NCHS}. & 2020-01-26 & State \\
  \bottomrule
\end{tabular}
\addtabletext{$^*$Available at $>60$\% of counties; $^{**}$available at
  20--60\% of counties; $^{***}$available at $<20$\% of counties.  For some
  signals, location availability varies over time, e.g., due to variable
  reporting volume.}
\label{tab:sources_signals}
\end{table*}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/time_trends_national.pdf}
  \caption{National trends, from April 2020 to April 2021, of four signals in
    the COVIDcast API. The auxiliary signals, based on medical claims data and
    massive surveys, track changes in officially reported cases quite
    well. (They have all been placed on the same scale as reported cases per
    100,000 people.)}
  \label{fig:time_trends_national}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/geo_wise_corr.pdf}
  \caption{Geo-wise correlations with case rates, from April 15, 2020 to April
    15, 2021, calculated over all counties for which all signals were available
    and which had at least 500 cumulative cases by the end of this period.}
  \label{fig:geo_wise_correlation}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/time_wise_correlation.pdf}
  \caption{Time-wise correlations with case rates, from April 15, 2020 to April
    15, 2021, calculated over all counties for which all signals were available
    and which had at least 500 cumulative cases by the end of this period.}
  \label{fig:time_wise_correlation}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/bexar_compare.pdf}
  \caption{Reported cases per day in Bexar County, Texas during the summer of
    2020. On July 16, 4,810 backlogged cases were reported, though they actually
    occurred over the preceding two weeks (this shows up as a prolonged spike in
    the left panel due to the 7-day trailing averaging applied to the case
    counts). Daily CTIS estimates of CLI-in-community showed more stable
    underlying trends.}
  \label{fig:bexar_compare}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/dv_as_of.pdf}
  \caption{Estimated percentage of doctor's visits due to COVID-like illness
    displayed across multiple issue dates, with later issue dates adding
    additional data and revising past data from prior issue dates.}
  \label{fig:dv_as_of}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/mobility-drop.pdf}
  \caption{Percentage point increase in SafeGraph estimates of the percentage of
  people staying completely at home, based on aggregated mobile device data,
  between March 1, 2020 and April 15, 2020.}
  \label{fig:mobility-drop}
\end{figure}

@@

\acknow{We thank Carrie Reed, Matt Biggerstaff, Michael Johansson, Rachel
  Slayton, Velma Lopez, Jo Walker and others on the CDC COVID-19 Modeling Team;
  Hal Varian, Brett Slatkin, and others on Google's Surveys team;
  Erin Hattersley, Rasmi Elasmar, and others at Google.org;
  Evgeniy Gabrilovich and others on Google's Health team;
  Curtiss Cobb and others on Facebook's  Demography and Survey Science, Data for
  Good and Health teams;
  Alex Smola and others at Amazon Web Services;
  Tim Suther and others at Change Healthcare;
  Paul Nielsen and others at Optum;
  John Tamerius and others at Quidel; and
  Ross Epstein and others at SafeGraph.
  This material is based on work supported by gifts from Facebook, Google.org,
  the McCune Foundation, and Optum; Centers for Disease Control and Prevention
  (CDC) grant U01IP001121; National Science Foundation Graduate Research
  Fellowship Program (NSF GRFP) award DGE1745016; and the Center for Machine
  Learning and Health (CMLH) at Carnegie Mellon.}

\showacknow{} % Display the acknowledgments section

% Bibliography
\bibliography{../../common/covidcast.bib}

>>>>

\documentclass[11pt]{article}
% Use the lineno option to display guide line numbers if required.

% \templatetype{pnasresearcharticle} % Choose template
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

\usepackage{authblk}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[numbers,square,sort&compress]{natbib}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{array}
\usepackage{lscape}

@@

% Middle authors
% \author[d]{Sumit Agrawal}
\author[e]{Wael Al Saeed}
\author[f]{Taylor Arnold}
\author[g]{Amartya Basu}
\author[h]{Jacob Bien}
\author[i]{{\'A}ngel A. Cabrera}
\author[b]{Andrew Chin}
\author[b]{Eu Jing Chua}
\author[b]{Brian Clark}
% \author[d]{Sarah Colquhoun}
\author[b]{Nat DeFries}
% \author[d]{David C. Farrow}
\author[i]{Jodi Forlizzi}
% \author[d]{Jed Grabman}
\author[b]{Samuel Gratzl}
\author[a]{Alden Green}
\author[b]{George Haff}
\author[i]{Robin Han}
% \author[d]{Kate Harwood}
\author[a,b]{Addison J. Hu}
% \author[d]{Raphael Hyde}
\author[h]{Sangwon Hyun}
\author[e]{Ananya Joshi}
\author[j]{Jimi Kim}
\author[i]{Andrew Kuznetsov}
\author[b]{Wichada La Motte-Kerr}
\author[k]{Yeon Jin Lee}
\author[l]{Kenneth Lee}
\author[b]{Zachary C. Lipton}
\author[i]{Michael X. Liu}
\author[m]{Lester Mackey}
\author[b]{Kathryn Mazaitis}
\author[n]{Daniel J. McDonald}
% \author[d]{Phillip McGuinness}
\author[o,p]{Balasubramanian Narasimhan}
% \author[d]{Michael P. O'Brien}
\author[a,b]{Natalia L. Oliveira}
\author[a,b]{Pratik Patil}
\author[i]{Adam Perer}
\author[b]{Collin A. Politsch}
\author[o]{Samyak Rajanala}
\author[e]{Dawn Rucker}
% \author[d]{Chris Scott}
\author[q]{Nigam H. Shah}
\author[r]{Vishnu Shankar}
\author[l]{James Sharpnack}
\author[b]{Dmitry Shemetov}
\author[s]{Noah Simon}
% \author[d]{Benjamin Y. Smith}
\author[b]{Vishakha Srivastava}
\author[n]{Shuyi Tan}
\author[o,p]{Robert Tibshirani}
\author[o]{Elena Tuzhilina}
\author[b]{Ana Karina Van Nortwick}
\author[a]{Val{\'e}rie Ventura}
\author[a,b]{Larry Wasserman}
% \author[d]{Benjamin Weaver}
\author[t]{Jeremy C. Weiss}
% \author[d]{Spencer Whitman}
\author[i]{Kristin Williams}

@@

\affil[a]{Department of Statistics \& Data Science, Carnegie Mellon University}
\affil[b]{Machine Learning Department, Carnegie Mellon University}
\affil[c]{Computational Biology Department, Carnegie Mellon University}
% \affil[d]{Google.org}
\affil[e]{Computer Science Department, Carnegie Mellon University}
\affil[f]{Linguistics Program, University of Richmond}
\affil[g]{Information Networking Institute, Carnegie Mellon University}
\affil[h]{Department of Data Sciences and Operations, University of Southern California}
\affil[i]{Human-Computer Interaction Institute, Carnegie Mellon University}
\affil[j]{School of Natural Sciences and Mathematics, University of Texas at Dallas}
\affil[k]{College of Fine Arts and Department of Psychology, Carnegie Mellon University}

@@

% Please add a significance statement to explain the relevance of your work
% \significancestatement{To study the COVID-19 pandemic, its effects on society,
%   and measures for reducing its spread, researchers need detailed data on the
%   course of the pandemic. Standard public health data streams suffer
%   inconsistent reporting and frequent, unexpected revisions. They also miss
%   other aspects of a population's behavior that are worthy of consideration. We
%   present an open database of COVID signals in the United States, measured at
%   the county level and updated daily. This includes traditionally reported COVID
%   cases and deaths, and many others: measures of mobility, social distancing,
%   internet search trends, self-reported symptoms, and patterns of COVID-related
%   activity in de-identified medical insurance claims. The database provides all
%   signals in a common, easy-to-use format, empowering both public health
%   research and operational decision-making.
% }

% Please include corresponding author, author contribution and author declaration information
% Googlers: SA, SC, DCF, JG, KH, RH, PM, MPO, CS, BYS, BW, SW
% \authorcontributions{Author contributions: A.R., L.B., M.J., A.R., J.T., A.C,
%   E.J.C., N.D., A.J.H., S.H., M.J., J.K., W.L.M.K, Z.C.L., L.M., N.L.O.,
%   J.C.W, R.R., and R.J.T. obtained and managed data;
%   A.R., J.B., J.F., Z.C.L., L.M., D.J.M., A.P., S.R., D.R., N.S., R.T.,
%   V.V., L.W., J.C.W, R.R., and R.J.T. designed software and
%   research;
%   A.R., L.B., M.J., A.R., J.T., W.A.S., T.A., A.B., J.B., L.B., A.A.C., A.C.,
%   E.J.C., B.C., N.D., S.G., A.G., G.H., R.H., A.J.H.,
%   S.H., M.J., A.J., J.K., A.K., M.X.L., L.M., K.M., D.J.M., B.N.,
%   N.L.O., P.P., C.A.P., S.R., V.S, J.S, D.S., N.S., V.S., S.T.,
%   J.T., R.T., J.C.W, and R.J.T. developed software;
%   W.A.S., A.C., B.C., S.G., G.H., K.M., D.J.M., B.N., J.S.,
%   D.S., and A.K.V.N. managed technical infrastructure and systems;
%   A.R., L.B., M.J., A.R., J.T, J.B., A.C., E.J.C., N.D.,  A.G.,
%   A.J.H., R.H., S.H., A.J., J.K., K.L., Y.J.L, Z.C.L., L.M., D.J.M., B.N.,
%   N.L.O., P.P., C.A.P., S.R., N.S., V.S., J.S., D.S., N.S., S.T., J.T., R.T.,
%   V.V., L.W., J.C.W., R.R., and R.J.T. performed research;
%   R.R. and R.J.T. acquired funding;
%   and A.R., L.B., M.J., A.R., J.T., and R.J.T. wrote the paper.
% }
% \authordeclaration{No competing interests to declare.}
% \correspondingauthor{\textsuperscript{1}To whom correspondence should be
%   addressed. E-mail: areinhar@stat.cmu.edu}
% \equalauthors{\textsuperscript{2}L.B., M.J., A.R., and J.T. contributed equally
%   to this work.}
\footnotetext[1]{To whom correspondence should be addressed. E-mail:
  areinhar@stat.cmu.edu}
\footnotetext[2]{L.B., M.J., A.R., and J.T. contributed equally to this work.}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
% \keywords{COVID-19 $|$ open data $|$ digital surveillance $|$ medical insurance
%   claims $|$ internet surveys}

\begin{document}
\maketitle

\clearpage

@@

Public health decision makers, healthcare providers, epidemiological
researchers, employers, institutions, and the general public benefit from
promptly and readily accessible data regarding COVID-19 activity levels,
countermeasures, and pandemic impact. Real-time indicators of COVID-19 activity
levels, such as statistics on cases, deaths, test positivity, and
hospitalizations, enable reports and interactive dashboard applications for
situational awareness \cite{Dong:2020, NYTimes, USAFacts}, and are essential for
most analyses of the pandemic. These data are available for locations across the
United States from a number of official sources and independent aggregators in
varied and inconsistent formats. Different data types and sources vary in
timeliness, based on when measured events occur in the progression of the
disease, testing capabilities, the reporting pipeline, and their publication
schedules.

@@

\begin{landscape}
\begin{table*}[t]
\centering
\caption{Data sources available in Delphi's COVIDcast API \cite{CovidcastAPI},
  as of date of publication. The first group of data sources are produced by
  Delphi from data not otherwise available publicly (or only available in
  limited form); the second group is mirrored from public sources.}
\begin{tabular}{>{\raggedright}p{1.2in} p{5.0in} l >{\raggedright\arraybackslash}p{0.5in}}
  \toprule
  \textbf{Data source} & \textbf{Signals available} & \textbf{First date} &
\textbf{Resolution} \\\midrule
  % Exclusive data
  Change Healthcare & Percentage of outpatient visits with COVID diagnostic
codes or codes indicating COVID-like symptoms. Based on de-identified claims
data processed by Change Healthcare. & 2020-02-01 & County$^*$ \\
  Doctor Visits & Percentage of outpatient visits primarily about COVID-like
symptoms, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^*$ \\
  Hospital Admissions & Percentage of new hospital admissions with COVID
diagnostic codes, based on de-identified claims data provided by health system
partners. & 2020-02-01 & County$^{**}$\\
  Quidel & Test positivity rates for COVID-19 antigen tests produced by
Quidel. & 2020-05-26 & County$^{**}$ \\
  SafeGraph & Mobility metrics, such as time away from home or visits to bars
and restaurants, based on cell phone mobility data collected by SafeGraph
\cite{SafeGraphSocial, SafeGraphPatterns}. & 2019-01-01 & County \\
  COVID-19 Trends and Impact Survey & COVID symptoms, social distancing
behaviors, mental health, economic impact, behavior (e.g., mask-wearing,
vaccination attitudes), and COVID testing signals based on daily surveys
conducted nationally by Delphi through Facebook \cite{DelphiSurvey,
Kreuter:2020}. & 2020-04-06 & County$^{**}$ \\
  \midrule
  % Mirrored data from other sources
  Health \& Human Services & Counts of hospital admissions due to confirmed or
suspected COVID-19, as reported by the Department of Health \& Human Services. &
2019-12-31 & State \\
  COVID Act Now & COVID-19 testing results, such as positivity rate and number
of tests, compiled by COVID Act Now from CDC reporting. & 2020-03-02 &
County$^*$ \\
  Google Symptoms & Trends in Google search volume for terms related to
anosmia and ageusia (loss of smell or taste), which correlate with COVID
activity, based on data shared by Google \cite{GoogleSymptoms}. & 2020-02-13 &
County$^{***}$ \\
  Cases and Deaths & Confirmed COVID-19 cases and deaths, compiled by JHU CSSE
\cite{Dong:2020} and by USAFacts \cite{USAFacts}. & 2020-01-22 & County \\
    NCHS Mortality & Weekly totals of deaths broken down by cause, such as
COVID, flu, or pneumonia, compiled by the National Center for Health Statistics
\cite{NCHS}. & 2020-01-26 & State \\
  \bottomrule
\end{tabular}
{\raggedright $^*$Available at $>60$\% of counties; $^{**}$available at
  20--60\% of counties; $^{***}$available at $<20$\% of counties.  For some
  signals, location availability varies over time, e.g., due to variable
  reporting volume.}
\label{tab:sources_signals}
\end{table*}
\end{landscape}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.6\columnwidth]{fig/time_trends_national.pdf}
  \caption{National trends, from April 2020 to April 2021, of four signals in
    the COVIDcast API. The auxiliary signals, based on medical claims data and
    massive surveys, track changes in officially reported cases quite
    well. (They have all been placed on the same scale as reported cases per
    100,000 people.)}
  \label{fig:time_trends_national}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.6\columnwidth]{fig/geo_wise_corr.pdf}
  \caption{Geo-wise correlations with case rates, from April 15, 2020 to April
    15, 2021, calculated over all counties for which all signals were available
    and which had at least 500 cumulative cases by the end of this period.}
  \label{fig:geo_wise_correlation}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.6\columnwidth]{fig/time_wise_correlation.pdf}
  \caption{Time-wise correlations with case rates, from April 15, 2020 to April
    15, 2021, calculated over all counties for which all signals were available
    and which had at least 500 cumulative cases by the end of this period.}
  \label{fig:time_wise_correlation}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.6\columnwidth]{fig/bexar_compare.pdf}
  \caption{Reported cases per day in Bexar County, Texas during the summer of
    2020. On July 16, 4,810 backlogged cases were reported, though they actually
    occurred over the preceding two weeks (this shows up as a prolonged spike in
    the left panel due to the 7-day trailing averaging applied to the case
    counts). Daily CTIS estimates of CLI-in-community showed more stable
    underlying trends.}
  \label{fig:bexar_compare}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.6\columnwidth]{fig/dv_as_of.pdf}
  \caption{Estimated percentage of doctor's visits due to COVID-like illness
    displayed across multiple issue dates, with later issue dates adding
    additional data and revising past data from prior issue dates.}
  \label{fig:dv_as_of}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{fig/mobility-drop.pdf}
  \caption{Percentage point increase in SafeGraph estimates of the percentage of
  people staying completely at home, based on aggregated mobile device data,
  between March 1, 2020 and April 15, 2020.}
  \label{fig:mobility-drop}
\end{figure}

@@

\subsection*{Acknowledgments}

We thank Carrie Reed, Matt Biggerstaff, Michael Johansson, Rachel Slayton, Velma
Lopez, Jo Walker and others on the CDC COVID-19 Modeling Team; Hal Varian, Brett
Slatkin, and others on Google's Surveys team; Erin Hattersley, Rasmi Elasmar,
and others at Google.org; Evgeniy Gabrilovich and others on Google's Health
team; Curtiss Cobb and others on Facebook's Demography and Survey Science, Data
for Good and Health teams; Alex Smola and others at Amazon Web Services; Tim
Suther and others at Change Healthcare; Paul Nielsen and others at Optum; John
Tamerius and others at Quidel; and Ross Epstein and others at SafeGraph. This
material is based on work supported by gifts from Facebook, Google.org, the
McCune Foundation, and Optum; Centers for Disease Control and Prevention (CDC)
grant U01IP001121; National Science Foundation Graduate Research Fellowship
Program (NSF GRFP) award DGE1745016; and the Center for Machine Learning and
Health (CMLH) at Carnegie Mellon.

% Bibliography
\bibliographystyle{unsrtnat}
\bibliography{../../common/covidcast.bib}

\clearpage

\appendix

\section*{Supplemental figures}

\clearpage

\input{supplement-medrxiv.tex}
